% $Id: nsf_data.tex 3061 2012-10-23 04:58:35Z jcarver $

This project will produce 4 types of data that require management:
\begin{enumerate*}
	\item{Results of SLR on SLRs}
	\item{Analysis of data from SLR author survey}
	\item{Analysis of existing SLR tools}
	\item{Output from community workshops}
\end{enumerate*}

\paragraph{Results of SLR on SLRs}
In the proposal, we describe a preliminary analysis of the published SLR papers. As part of the proposed work, we will analyze each published SLR in detail. The results of the analysis will be a data extraction sheet for each published SLR. We will make these data extraction sheets available on the project website.

\paragraph{Analysis of data from SLR author survey}
In the proposal, we describe an analysis of a portion of the data gathered from our SLR author survey. As part of the proposed work, we will perform a much deeper analysis of that data. This analysis will include a the quantitative analysis along with a detailed description of the qualitative results from the survey. We will make the results of this analysis available on the project website.

\paragraph{Analysis of existing SLR tools}
In the proposal, we provide a high-level description of the existing SLR tools, based upon information available through published papers or websites. As part of the proposed work, we plan to interact with the tools in more detail (downloading them where possible). We will analyze, in detail, how these tools address a portion of the requirements for our proposed infrastructure. We will document the results of this analysis on the project website. 

\paragraph{Output from community workshops}
We plan to conduct two community workshops to gather data about our preliminary requirements and our proposed solution. These workshops will be highly-interactive with the goal of generating concrete results that we can incorporate into our proposed infrastructure. For each workshop we plan to document the following information:
\begin{enumerate*}
	\item{Input to workshop (i.e. proposed requirements or proposed solution}
	\item{Workshop attendees}
	\item{Summary of the discussion at the workshop}
	\item{Output of the workshop (i.e. revised requirements or revised solution}
\end{enumerate*}

\textbf{Policies for Access and Sharing}
Data gathered during the project will be made freely available on the project website. Any data that could have personally-identifiable information will be anonymized prior to posting. If workshop attendees do not wish their identity to be known, this information will be redacted from the website.

\textbf{Policies for Reuse}
Data extraction sheets from the SLR analysis will be available for other researchers to reuse. Detailed findings will be available as technical reports and published research reports.

% vim:syntax=tex
