% $Id: nsf_budget.tex 3066 2012-10-23 13:38:42Z jcarver $

\subsection*{A. Senior Personnel}

The budget includes summer support for the senior personnel as follows: 0.4 months for Dr.\ Carver, 0.4 months for Dr.\ Kraft, and 0.09 months for Dr. Hale. All three will be involved in the management of the project activities and the planning of the community interactions.

\subsection*{B. Other Personnel}

The budget includes support for the other personnel as follows:
three summer months for one graduate research assistant (GRA) from Management Information Systems at \$3,000 per month and
one calendar year for one GRA from Computer Science at \$1,750 per month.
The monthly rate of \$3,000 is the standard rate for Ph.D. students
in the Management Information Systems Program, and
the monthly rate of \$1,750 is the standard rate for Ph.D. students
in the Department of Computer Science.

\subsection*{C. Fringe Benefits}

Fringe benefits were calculated based on the salary of the PI and Co-PI at the rate of 32\% for the summer. This rate includes FICA, state retirement, SUI, and insurance. Fringe benefits for the graduate student include the FICA rate of 7.7\% for the summer period only. Insurance for the graduate students is \$1,348/year.

\subsection*{D. Equipment}
No equipment is requested.

\subsection*{E. Travel}

Travel funds are requested for the PI, Co-PIs and graduate students to attend the workshops in which community interaction will be performed. Those workshops will occur at international software engineering conferences including: The International Conference on Software Engineering (ICSE), The International Symposium on Empirical Software Engineering and Measurement (ESEM), and The International Conference on Evaluation and Assessment in Software Engineering (EASE).

\subsection*{G. Other Direct Costs}

\subsubsection*{1. Materials and Supplies}

The materials and supplies budget includes modest support for books and other resources.

\subsubsection*{6. Other}

The budget includes funds to cover the tuition of one GRA for one academic year.

\subsection*{I. Indirect Costs}

Indirect costs are calculated at the approved rate of 47\% MTDC

\subsection*{L. Amount of This Request}

The total amount of this request is \$100,000.

% vim:syntax=tex
