% $Id: part_concept.tex 3089 2012-10-23 21:38:10Z nkraft $

\emph{Systematic Literature Reviews (SLR)} are useful for drawing conclusions about about a phenomenon, based upon the current state of published evidence.
Although SLRs are increasingly recognized as vital to the software engineering (SE) discipline,
%there are still barriers that inhibit more widespread popularity.
there are still barriers inhibiting widespread adoption of SLRs within the SE community.
%barriers still inhibit widespread adoption of SLRs within the SE community.
%These barriers are the result of the lack of infrastructure to support the effort-intensive, largely manual SLR process. With the frequency of empirical studies, the SE domain is well-suited for SLRs. The primary goal of this CI-P proposal is to create an infrastructure to support the SLR process. Our target community ("the community") contains SE researchers who already conduct SLRs and SE researchers who will be more likely to conduct SLRs if the barriers are removed. Based upon our preliminary work, the primary objectives of this CI-P proposal are to: 
These barriers remain due to the lack of infrastructure support for the effort-intensive, largely manual SLR process.
%With the frequency of empirical studies, the SE domain is well-suited for SLRs.
Given the frequency of empirical studies in SE, the domain is well-suited for SLRs.
The primary goal of this CI-P project is to propose an infrastructure to support the SLR process.
Our target community (``the community'') comprises SE researchers who already conduct SLRs, as well as SE researchers who will be more likely to conduct SLRs if the barriers are removed. Building on our preliminary work, the primary objectives of this CI-P project are to: 
\begin{itemize*}
	%\item{Iterate on the Community Needs by eliciting, validating, and prioritizing the requirements for the SLR infrastructure and propose a new SLR support infrastructure}
	\item{Elicit, validate, and prioritize the requirements for an SLR support infrastructure}
   \item{Propose a new SLR support infrastructure based on those requirements}
	\item{Create a detailed plan for the development and deployment of the infrastructure}
\end{itemize*}

\vspace*{-4pt }

After completion of these planning activities, we estimate that it will take approximately three years and \$500,000 to develop and deploy the infrastructure. Once deployed, it should require minimal maintenance, which will consist primarily of ensuring compatibility with software upgrades. Therefore, the ongoing operation costs should be easily managed with internal resources. We anticipate the infrastructure to have an indefinite lifetime because review of existing literature is, and will continue to be, an integral part of any new research endeavor. 

% vim:syntax=tex
