% $Id: sec_needs.tex 3080 2012-10-23 19:33:43Z jcarver $

\vspace*{-4.5pt}
This section describes our plan to identify the consensus needs of the community
by supplementing and improving the preliminary community needs described in Section~\ref{sec:prelim:needs}
and by validating and prioritizing the improved community needs.
Our plan comprises the following tasks:
\begin{itemize*}
\setlength\itemindent{-1.15em}
\vspace*{-4.5pt}
\item[] \textbf{Data Collection and Analysis}
   \begin{enumerate*}
   \setlength\itemindent{-1.4em}
   \vspace*{-3pt}
   \item[T1.] Extract additional process details from published SLRs
   \item[T2.] Code additional survey responses from SLR authors
   \item[T3.] Analyze the extracted process details and coded survey responses
   \end{enumerate*}
\vspace*{-3pt}
\item[] \textbf{Evolution of Identified Community Needs}
   \begin{enumerate*}
   \setlength\itemindent{-1.4em}
   \vspace*{-3pt}
   \item[T4.] Supplement the preliminary community needs based on the analysis results
   \item[T5.] Solicit community feedback on the supplemented needs
   \item[T6.] Improve the supplemented community needs based on the community feedback
   \end{enumerate*}
\vspace*{-3pt}
\item[] \textbf{Validation and Prioritization of Identified Community Needs}
   \begin{enumerate*}
   \setlength\itemindent{-1.4em}
   \vspace*{-3pt}
   \item[T7.] Validate the improved community needs  using community evaluation
   \item[T8.] Solicit community input on the prioritization of the validated community needs 
   \item[T9.] Prioritize the validated community needs based on the community input
   \end{enumerate*}
   \vspace*{-9pt}
\end{itemize*}

\vspace*{-6pt}
Tasks T5 and T7 involve workshop organization.
The following paragraphs describe the workshop agendas.
Before each workshop we will post an announcement to the SEWORLD mailing list and send invitations to SLR authors.
We will also contact survey respondents that have expressed interest in this project.
After each workshop we will document activities and outcomes, post them to the project Wiki, and announce their availability.

\paragraph{Data Collection and Analysis}
Tasks T1--T3 involve the improvement of our preliminary analysis of process details from the published SLRs and survey responses from the SLR authors.
Task~T1 is to improve our preliminary analysis of the 214 published SLRs described earlier.
We will extract additional process details from each of the published SLRs to permit a more complete
analysis of the SLR process, including the difficulties that authors face and the strategies that they use to ease those difficulties.
%Task T2 is to improve our preliminary analysis of the 50+ survey responses that we received from authors of published SLRs.
Task T2 is to improve our preliminary analysis of the 50+ responses to our SLR author survey.
We will code additional author responses from each of the survey responses to permit a more complete
analysis of SLR process data, %the difficulties faced and of the needs identified by the respondents.
including labor-intensive, automatable process phases. %or in need of tool support.
Task T3 is to analyze all collected data. %results of Tasks T1 and T2.

\paragraph{Evolution of Identified Community Needs}
Tasks T4--T6 involve the evolution of the preliminary community needs. % (Section~\ref{sec:prelim:needs}).
Task T4 is to supplement the preliminary community needs based on the results of Task T3.
We will both refine existing and formulate new community needs based on the analysis results.
Task T5 is to solicit community feedback on the supplemented community needs that result from Task T4.
We will organize a half-day workshop at the 2013 International Conference on Software Engineering (ICSE'13). %,
%to be held May 2013 in San Francisco, CA.
Because an award notification would arrive just before the conference (in May),
participation is likely to be limited to those already planning to attend ICSE'13.
Thus, we will contact colleagues directly to request their feedback. %via other channels such as email and the project Wiki.
Task T6 is to improve the supplemented community needs based on the community feedback from Task T5. %we receive. %workshop outcomes.
%We will integrate suggestions from workshop participants and other community members who provide feedback via email or the project Wiki.

\paragraph{Validation and Prioritization of Community Needs}
Tasks T7--T9 involve the validation and prioritization of the improved community needs that result from Task T6.
Task T7 is to validate the improved community needs with help from the community.
We will organize a workshop at the 2013 International Symposium on Empirical Software Engineering and Measurement (ESEM).
During the day-long workshop, participants will refine and validate the improved community needs via a series of evaluation activities.
Time permitting, we will solicit participant input on the prioritization of the validated community needs.
Task T8 is to solicit additional community input related to prioritization of community needs.
We will solicit this input via a survey. %of community members.
Task T9 is to prioritize the validated community needs based on the community input from Task T8.
%We will integrate the results of Task T8.


% vim:syntax=tex
