% $Id: sec_tools.tex 3081 2012-10-23 19:36:23Z jcarver $


%\item Review of Cochrane Tool

\vspace*{-4.5pt}
In this section we describe our plan
to identify the major characteristics and features of the infrastructure
by updating, supplementing, and refining the infrastructure proposal described in Section~\ref{sec:prelim:tools}
and by prioritizing the characteristics and features included in the infrastructure proposal.
Our plan comprises the following tasks:
\begin{itemize*}
%\makeatletter
%   \setlength{\leftskip}{-\@totalleftmargin}
%   \addtolength{\leftskip}{6pt}
%\makeatother
\setlength\itemindent{-1.15em}
\vspace*{-4.5pt}
\item[] \textbf{Infrastructure Evolution}
   \begin{enumerate*}
   \setlength\itemindent{-1em}
   \vspace*{-3pt}
   \item[T10.] Update the infrastructure proposal based on the validated, prioritized community needs
   \item[T11.] Solicit community feedback on the updated infrastructure proposal
   \item[T12.] Supplement the updated infrastructure proposal based on the community feedback
   \item[T13.] Refine the supplemented infrastructure proposal using community evaluation
   \end{enumerate*}
\vspace*{-3pt}
\item[] \textbf{Characteristic and Feature Prioritization}
   \begin{enumerate*}
   \setlength\itemindent{-1em}
   \vspace*{-3pt}
   \item[T14.] Solicit community input on the prioritization of the proposed characteristics and features
   \item[T15.] Prioritize the proposed characteristics and features based on community input
   \end{enumerate*}
   \vspace*{-9pt}
\end{itemize*}

\vspace*{-6pt}
Task T13 involves workshop organization.
The following paragraphs describe the workshop agenda.
We will publicize the workshop and record its activities and outcomes
in the same manner as described in the previous section.

\paragraph{Infrastructure Evolution}
Tasks T10--T13 involve the improvement of the infrastructure proposal.
Task~T10 is to update the infrastructural proposal based on the results of Task 9 (from the previous section).
We will both refine existing and define new characteristics and features based on the validated, prioritized community needs.
Task~T11 is to solicit community feedback on the updated infrastructure proposal that results from Task T10.
We will request feedback from individuals who contributed to the identification of community needs and
participated in the community needs validation and prioritization process.
Task~T12 is to supplement the updated infrastructure proposal based on the results of Task T11.
We will both refine existing and define new characteristics and features based on the community feedback.
Task~T13 is to refine the supplemented infrastructure proposal with help from the community.
We will organize a workshop at the 2014 International Conference on Evaluation and Assessment in Software Engineering (EASE'14) or at ICSE'14.
During the day-long workshop, participants will refine the supplemented infrastructure proposal via a series of evaluation activities.
Time permitting, we will also solicit participant input on the prioritization of the proposed characteristics and features.

\paragraph{Characteristic and Feature Prioritization}
Tasks T14 and T15 involve the prioritization of the characteristics and features included in the refined infrastructure proposal
that results from Task T13.
Task T14 is to solicit additional community input related to the prioritization of the proposed characteristics and features.
We will solicit this input via a survey.
Task T15 is to prioritize the proposed characteristics and features based on the community input from Task T14.

% vim:syntax=tex
