\subsection*{A. Senior Personnel}
\noindent
1.5 summer months per year is requested for PI Carver. 
This time will be spent supervising supervising the graduate students, conducting case studies, and guiding the development of the infrastructure..
The monthly salary for the PI for year 1 is calculated based on dividing his current 9-month salary by 9 and inflating by 5\%. 
A 5\% inflation is built in for subsequent years. 
\vspace{8pt}

\subsection*{B. Other Personnel}
\noindent
Funds are requested to support 3 graduate students. 
The annual stipend for the graduate student is \$24,000.
The graduate students will perform tool development, content development, case studies, and evaluation. 
\vspace{8pt}

\subsection*{C. Fringe Benefits}
\noindent
Fringe benefits are calculated based on the salary of the PI at the rate of 32\% for the summer. 
This rate includes FICA, state retirement, SUI, and insurance. 
Fringe benefits for the graduate student include insurance and the FICA rate of 7.7\% for the summer period only. 
\vspace{8pt}

\subsection*{D. Equipment}
\noindent
No equipment is requested.
\vspace{8pt}

\subsection*{E. Travel}
\noindent
Travel funds are requested for the PI and/or students travel to conferences to conduct case studies, hold relevant workshops, and meet with collaborators. 
Examples of conferences include: ESEM, FSE, and ICSE.
Travek funds are also requested for the PI to attend the PI meeting.
\vspace{8pt}

\subsection*{F. Participant Support}
\noindent
\$10,000 is requested in each of years 1 and 3 to support participant travel to a workshop.
The funds will be used to pay for the flight, hotel, and other expenses associated with travel for SLR researchers to participate in workshops to learn about the infrastructure and to provide feedback on the infrastructure.
\vspace{8pt}

\subsection*{G. Other Direct Costs}
\vspace{8pt}

\subsubsection*{1. Materials and Supplies}
\noindent
Funds are to purchase books and materials related to the grant. 
Funds are also requested for producing posters or other materials to disseminate the results of the project.
\vspace{8pt}

\subsubsection*{6. Other}
\noindent
Tuition is requested for the graduate student at the current tuition rate plus an estimated 5\% annual increase. 
A 5\% annual increase is built in for subsequent years.
\vspace{8pt}\\

\subsection*{I. Indirect Costs}
\noindent
Indirect costs are calculated at the approved rate of 49\% MTDC.
\vspace{8pt}\\

\subsection*{L. Amount of This Request}
\noindent
Total Amount of Request: \$718,709