\subsection*{A. Senior Personnel}

The budget includes summer support for the senior personnel as follows: 1 months for Dr.\ Carver, .6 months for Dr. Hale, and 2 months for Dr. Hassler. All three will be involved in the management of the project activities and the planning of the community interactions.

\subsection*{B. Other Personnel}

The budget includes support for the other personnel as follows:
Two graduate students to support the architecture, high-level design, and provide input to management of the CAPS developer teams.
The graduate students salary is \$24,000/year.
Insurance for the graduate students is \$1,200/year.

\subsection*{C. Fringe Benefits}

Fringe benefits were calculated based on the salary of the PI, Co-PI and Senior Personnel at the rate of 32\% for the summer. This rate includes FICA, state retirement, SUI, and insurance. Fringe benefits for the graduate students include the FICA rate of 7.7\% for the summer period only. 

\subsection*{D. Equipment}
No equipment is requested.

\subsection*{E. Travel}

Travel funds are requested for the PI, Co-PI, Senior Personnel and graduate students to travel to conferences to present intermediate and final results and to recruit additional users.
In addition, money is allocated in years 2 and 3 to allow the PI, Co-PI, Senior Personnel and graduate students to attend the community workshops.
Those workshops and paper presentations will occur at international software engineering conferences including: The International Conference on Software Engineering (ICSE), The International Symposium on Empirical Software Engineering and Measurement (ESEM), and The International Conference on Evaluation and Assessment in Software Engineering (EASE).

\subsection*{G. Other Direct Costs}

\subsubsection*{1. Materials and Supplies}

Funds are requested to support cost of hosting the infrastructure on the University of Alabama's Office of Information Technology servers.

\subsubsection*{6. Other}

The budget includes funds to cover the tuition for the graduate students.
The budget also includes funds in years 2 and 3 to organize community workshops. These funds will be used to provide travel support to encourage participation from a large segment of the target population.
The budget includes \$80,000/year to hire CAPS development staff to implement portions of SAInT. At \$60/hour, this amount equals .67 FTEs/year

\subsection*{I. Indirect Costs}

Indirect costs are calculated at the approved rate of 49\% MTDC

%\subsection*{L. Amount of This Request}

%The total amount of this request is \$998,287.