\paragraph{Types of Data}
This research will produce public source code; example text/structured data sets; predictive models; predictive model's intermediate tuning cache ;records of results of applying the code to the data; and work-processing files (the reports of our results) and quantitative survey results.
\vspace{8pt}

\paragraph{Standards for data and metadata format}
All data will be stored in different format, appropriate for the type of data being stored. For example, appropriate data formats for papers include word files, latex files, and PDF files. As another example, appropriate data formats for repository data including Attribute Relation File Format (.arff) or Comma-Separated Values (.csv). Similarly Hierarchical Data Format (.h5) or Pickle(.pkl) for storing generated models. 
\vspace{8pt}

\noindent
All our scripts used here will be based around software tools in widespread use (GitHub, Travis CI, etc.). We will release all our tools via open source licenses, so our results can be readily applicable to researcher or developers using GitHub, etc. 
\vspace{8pt}

\paragraph{Policies for access and sharing}
Where possible, open source data and software will be shared public through repository (with an exception for qualitative survey results which may be presented as survey summary after applying de-identification of the responses from individuals). Repository data will be freely available to the world and licensed under a Creative Commons Attribution 4.0. International license (https://creativecommons.org/ licenses/by/4.0/). This data will be made freely available our repository, accessible through the internet. 
\vspace{8pt}

\noindent
We acknowledge that, sometimes, researchers  and Model
Store app developers
may not wish to publicly share their hard-won data. For those researchers and users, we will respect their wishes. Also we might  collect data and pre-build models from ModelDepot under Non-Disclosure agreement. We will respect those agreements and not share those publicly.That said, we will encourage them to consider a (say) six month embargo rule. I.e. they have the only access to the day for (say) six months while they write their papers (and after that, the data can go public.). 
\vspace{8pt}



\paragraph{Policies and provisions for re-use, re-distribution, and derivatives}
All published and open source data may be re-used, re-distributed, and derived as long as the original data is not misrepresented, and the materials do not violate the acceptable use of the IP holders. Others may change or alter the open source data for personal purposed provided that these changes are made clear in any publications, re- distributions, or derivations. 
\vspace{8pt}

\paragraph{Plans for archiving data and other research products}
Repository data will be hosted on Zenodo repository (hosted at the Large Hadron Collider in Switzerland). Papers will be published at major conference and journals in SE data analytics.